Estimating Information Transfer in Hard Parameter Sharing via Precise Bias-variance Asymptotics

### 2021-07-17 revision_journal/exp.tex
finish sec 4

\begin{algorithm}[!h]
	\caption{Progressive training of hard parameter sharing networks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$.
		\Param A shared module $B$, and output layers $A_1, A_2$.
		\Req Number of batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; A_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, A_2$ optimized for task $2$.
		\State Divide $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
		\For{$j = 1,\dots, T$}
		\State Minimize the cross-entropy loss of $B, A_1, A_2$ on $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X^{(2)}, Y^{(2)})$ using SGD.
		\EndFor
		\State Let $a_i = \hat{g}(B; A_2)$ be the validation accuracy.
		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
		\State \textbf{break}
		\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

\begin{wrapfigure}[9]{r}{0.3\textwidth}
	\vspace{0.0in}
	\centering
	\begin{tabular}{c c c}
		\toprule
		Models & Relative cost \\
		\midrule
		{\bf CNN}  & 30\% \\
		{\bf LSTM} & 35\% \\
		{\bf MLP}  & 31\%  \\
		\bottomrule
		\end{tabular}
		\captionof{table}{The computational cost of running Algorithm \ref{alg_inc_train} relative to the cost of running SGD.}
		\label{tab:taskonomy}
	\label{fig_intro_arch}
\end{wrapfigure}
We evaluate Algorithm \ref{alg_inc_train} under two scenarios.
First, we consider all $15$ pairwise tasks and use the first task as a data source to help predict the second task.
We find that when averaged over all $15$ two-task pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
Second, we consider using all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
We find that a similar progressive training style procedure requires less than $35\%$ of the computational cost for reaching the same average test accuracy compared to SGD.

\medskip
\noindent\textit{Further details.}
Algorithm \ref{alg_inc_train} uses SGD during the minimization step.
We randomly shuffle the data of both tasks and apply SGD on the shuffled data.
For the two-task experiment, we set $\tau$ to be task two's (STL) test accuracy trained without using any other task's data.
%We include all of task two's data and progressively add task one's data using the procedure described above.
As a result, once Algorithm \ref{alg_inc_train} terminates, task two's test accuracy is at least $\tau$.
For the six-task experiment, We set $\tau$ to be the average test accuracy of all six tasks trained using all tasks' data.
We include the data from all tasks except SST. For SST, we progressively increasing its sample size similar to Algorithm \ref{alg_inc_train}.

>>>>

\begin{algorithm}[!h]
	\caption{Progressive training of hard parameter sharing networks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X^{(1)}, Y^{(1)})$ and $(X^{(2)}, Y^{(2)})$, divided into a training, validation, and test set.
		\Param A shared module $B$, and output layers $A_1, A_2$.
		\Req Number of batches $S$, epochs $T$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, A_2$ optimized for task two.
		\State Divide the training set of $(X^{(1)}, Y^{(1)})$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
		\For{$j = 1,\dots, T$}
		\State Minimize the cross-entropy loss of $B, A_1, A_2$ on  $\set{(x^{(k)}, y^{(k))}}_{k=1}^i$ and the training set of $(X^{(2)}, Y^{(2)})$ using SGD.
		\EndFor
		\State Let $a_i$ be the current validation accuracy for task two.
		\If{$a_i < a_{i-1}$ or $a_i > \tau$}
		\State \textbf{break}
		\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

\smallskip
\begin{wrapfigure}[10]{r}{0.26\textwidth}
	\vspace{-0.15in}
	\centering
	\begin{tabular}{c c c}
		\toprule
		Models & Relative cost \\
		\midrule
		{\bf CNN}  & 30\% \\
		{\bf LSTM} & 35\% \\
		{\bf MLP}  & 31\%  \\
		\bottomrule
		\end{tabular}
		\captionof{table}{The computational cost of running Algorithm \ref{alg_inc_train} relative to the cost of running SGD.}
		\label{tab:taskonomy}
	\label{fig_intro_arch}
\end{wrapfigure}
We evaluate Algorithm \ref{alg_inc_train} in two scenarios.
First, we consider transferring from single data source to a target task.
We evaluate over all $15$ two-task pairs.
We find that when averaged over all the pairs, our procedure requires less than $35\%$ of the computational cost relative to SGD while reaching the same level of test accuracy for predicting task two.
Second, we consider transferring from multiple data sources.
We use all six datasets as data sources to help predict every other task---that is, we measure the average accuracy of predicting all six tasks.
We find that a similar progressive training style procedure requires less than $35\%$ of the computational cost (relative to the cost of running SGD) for reaching the same average test accuracy of SGD.

\medskip
\noindent\textit{Further details.}
Algorithm \ref{alg_inc_train} uses SGD during the minimization step.
We randomly shuffle the data of both tasks and apply SGD on the shuffled data.
For the two-task experiment, we set $\tau$ to be task two's (STL) test accuracy trained without using any other task's data.
%We include all of task two's data and progressively add task one's data using the procedure described above.
%As a result, once Algorithm \ref{alg_inc_train} terminates, task two's test accuracy is at least $\tau$.
For the six-task experiment, We set $\tau$ to be the average test accuracy of all six tasks trained using all tasks' data.
We include the data from all tasks except SST. For SST, we progressively increasing its sample size similar to Algorithm \ref{alg_inc_train}.
